Dirichlet discretization of Neumann problems

### 2020-01-06 paper_lap/01intro.tex
adding numerical and small changes to intro and section 2

\section{Introduction}
Laplace's equation arises in a vast array of contexts (classical electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs). As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable. Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), representing the solution to the boundary value problem as the potential produced by charges (single-layer potentials) or dipoles (double-layer potentials) on the boundary of the domain. Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE. When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see \cite{hao}, for example).

@@

 Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{} with poles exponentially clustered near the corners. While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches, and have difficulties handling complicated domains and boundary data.

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{}. In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on the adjoint method \cite{}. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.

>>>>

\section{Introduction}
Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs). As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable. Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), where the solution to the boundary value problem is represented by layer potentials on the boundary of the domain. Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE. When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see \cite{hao}, for example).

@@

 Another class of methods is based on approximating the solution to the two-dimensional problem by rational functions \cite{} with poles exponentially clustered near the corners. While this approach allows for fast evaluation of the solution near the boundary of the domain, current implementations are specialized to two-dimensions, are significantly slower than other approaches for large problems, and have difficulties handling complicated domains and boundary data.

 Finally, a recent approach is based on leveraging explicit representations of the solutions to the BIEs in the vicinity of the corner as sums of fractional powers depending on the angle \cite{}. Using these representations one can construct high-order discretizations which introduce relatively few extra degrees of freedom near the corners (i.e. an amount which is comparable to the number required for smooth portions of the boundary). This approach has been used to generate efficient discretizations for Dirichlet problems for Laplace's equation on polygonal domains\cite{}.

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on the adjoint method \cite{}. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.

### 2020-01-06 paper_lap/02mprelim.tex
adding numerical and small changes to intro and section 2

\section{Mathematical preliminaries}
\subsection{Boundary value problems}
Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
unit normal $\bnu: \Gamma \to S^1,$ as well as a function 
$f: \Gamma \to \mathbb{R},$ we consider 
the following four boundary value problems.

>>>>

\section{Mathematical preliminaries}
\subsection{Boundary value problems}
Given a polygonal domain  $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma$ and outward-pointing 
unit normal $\bnu$, as well as a function 
$f: \Gamma \to \mathbb{R},$ we consider 
the following four boundary value problems.
